Preprocessing

### 2023-08-31 analysis/preprocessing.Rmd
Update preprocessing.Rmd

```{r}
d_journals <- d_journals %>%
  filter(!(journal == "HUMAN ARENAS" & timestamps == "8/6/2023 3:37:26"))
```

@@

```{r}
d_journals <- d_journals %>%
  filter(!(journal == "INFANTS & YOUNG CHILDREN" & timestamps == "7/15/2023 18:51:15"))
```

@@

```{r}
d_journals <- d_journals %>%
  filter(!(journal == "EDUCATIONAL PSYCHOLOGIST" & timestamps == "6/29/2023 14:06:13"))
```

@@

```{r}
d_journals <- d_journals %>%
  filter(!(journal == "EUROPEAN JOURNAL OF PERSONALITY" & timestamps == "6/29/2023 22:01:35"))
```

@@

```{r}
d_journals <- d_journals %>%
  filter(!(journal == "PERSONALITY AND SOCIAL PSYCHOLOGY REVIEW" & timestamps == "7/3/2023 18:34:38"))
```

@@

```{r}
d_journals <- d_journals %>%
  filter(!(journal == "PSYCHOLOGICAL MEDICINE" & timestamps == "8/6/2023 9:49:10"))
```

@@

d_journals %>%
  group_by(journal) %>%
  mutate(has_final = any(coder_id == "FINAL (TEH)"))

>>>>

```{r}
d_journals <- d_journals %>%
  filter(!(journal == "HUMAN ARENAS" & timestamps == "8/6/2023 3:37:26" & coder_id != "FINAL (TEH)"))
```

@@

```{r}
d_journals <- d_journals %>%
  filter(!(journal == "INFANTS & YOUNG CHILDREN" & timestamps == "7/15/2023 18:51:15" & coder_id != "FINAL (TEH)"))
```

@@

```{r}
d_journals <- d_journals %>%
  filter(!(journal == "EDUCATIONAL PSYCHOLOGIST" & timestamps == "6/29/2023 14:06:13" & coder_id != "FINAL (TEH)"))
```

@@

```{r}
d_journals <- d_journals %>%
  filter(!(journal == "EUROPEAN JOURNAL OF PERSONALITY" & timestamps == "6/29/2023 22:01:35" & coder_id != "FINAL (TEH)"))
```

@@

```{r}
d_journals <- d_journals %>%
  filter(!(journal == "PERSONALITY AND SOCIAL PSYCHOLOGY REVIEW" & timestamps == "7/3/2023 18:34:38" & coder_id != "FINAL (TEH)"))
```

@@

```{r}
d_journals <- d_journals %>%
  filter(!(journal == "PSYCHOLOGICAL MEDICINE" & timestamps == "8/6/2023 9:49:10" & coder_id != "FINAL (TEH)"))
```

@@

d_journals %>%
  group_by(journal) %>%
  mutate(has_final = any(coder_id == "FINAL (TEH)")) %>%
  filter(has_final == F) %>% View()
